Dispersion distance and the matter distribution of the Universe in dispersion space

### 2015-06-04 writeup/dm_space_distortions.tex
mention one-point statistics in paragraph intrinsic/stocastic DM

Perhaps, more concerning is the dispersion from the source's immediate environment
as well as the halo in which it resides. These electrons will presumably be
clustered around the source on scales far smaller than the survey
resolution and are thus not accounted for in the
$\delta_e$--$\delta_f$
correlations included in the above formalism.  This will have a mean
contribution, common to all sources and which may be epoch dependant, that will
modify the mean dispersion--distance relation. This will need to be calibrated in some
way or else fit with nuisance parameters during parameter estimation.  There
will also be a stochastic piece which varies from source to source.  This will
limit the precision at which $\chi_s$ can be measured, thus limiting the
resolution of dispersion space density maps in the radial direction.

Detailed treatment of the above complications is beyond the scope of this
work. The magnitude of the contribution from the progenitor is at present
unknown. To crudely deal with it here we use relatively large
bins widths of $\Delta\chi = 100\,{\rm Mpc}/h$
and exclude the $\chi = \chi'$ bin pairs.
Because the local term drops rapidly with radial separations, this effectively 
discards the contribution from the local term which is most sensitive to having
precise radial distances.

>>>>

Perhaps, more concerning is the dispersion from the source's immediate environment
as well as the halo in which it resides. These electrons will presumably be
clustered around the source on scales far smaller than the survey
resolution and are thus not accounted for in the
$\delta_e$--$\delta_f$
correlations included in the above formalism.  This will have a mean
contribution, common to all sources and which may be epoch dependant, that will
modify the mean dispersion--distance relation. This will need to be calibrated in some
way or else fit with nuisance parameters during parameter estimation.  
will also be a stochastic piece which varies from source to source.  This will
limit the precision at which $\chi_s$ can be measured, thus limiting the
resolution of dispersion space density maps in the radial direction.  However, we note that one-point statistics from the same dataset that is used to calculate clustering
should provide empirical information about these properties independent of their physical origin.

Detailed treatment of the above source modelling is beyond the scope of this
work. The magnitude of the contribution from the progenitor is at present
unknown. To crudely deal with it here we use relatively large
bins widths of $\Delta\chi = 100\,{\rm Mpc}/h$
and exclude the $\chi = \chi'$ bin pairs.
Because the local term drops rapidly with radial separations, this effectively 
discards the contribution from the local term which is most sensitive to having
precise radial distances.
